\section{Introduction} \label{sec:intro}
A zero knowledge protocol tries to convince a verifier about the truth of a
statement, without revealing any additional information. Availability of
practically efficient zero knowledge protocols is enabling their real-life
application. These include proving the correctness of
transactions in cryptocurrencies such as \cite{zerocash} or validating sensitive web browser data reported during
telemetry \cite{MozillaPrio}. Still in the dream of a decentralized world, there are
multiple co-opetitive entities i.e.,
collaborating but mutually distrusting entities interacting with each other to obtain insights
and maximize their goals. We envisage applications of zero knowledge
proofs to enable these mutually
distrusting entities to prove a claim on their joint data. In this setting, the 
traditional zero knowledge protocols are restrictive since they require
a single prover to have the entire witness needed to generate the proof. 

%\pdnote{do we want to motivate it in a way such that the honest prover setting we are looking at will suffice for the listed applications? }
In this work, we study the general setting of \textit{distributed prover
zero-knowledge protocols} ($\DPZK$) where multiple co-opetitive entities each possessing their own secret
data want to prove to a verifier that their secret data together satisfies a
predicate of common interest. This is to be done without revealing any information
about their sensitive data to each other or to the verifier. We illustrate
through some  real-world applications: %potential
\begin{itemize}
\item A simple but pertinent scenario is of a \textit{joint loan application} by an association of companies from a particular industry. The loan issuer has a set of financial requirements that it wants the association to satisfy, but there is no single trusted entity to act as the prover whom all the companies are willing to provide their sensitive business information with.
\item In cryptocurrency settings \cite{bitcoin, ethereum, zerocash}, this would enable a \textit{multi-wallet transaction} where the wallets are held by different parties or a \textit{proof of joint stake} where the stake is held by different parties. These in turn enable secure collaboration applications by design on a blockchain network. % use it for joint auction-
\item In trade logistics business networks \cite{scbn, e2open, tradelens}, a major reason for businesses to enter these networks is to benefit from cross-industry statistics. Publishing these statistics in a publicly verifiable manner without having a single trusted entity is another embodiment of this setting.
\end{itemize}

Formally, we have multiple provers $\prover_1, \ldots, \prover_{\Num}$
respectively possessing witnesses $\wit_1, \ldots, \wit_{\Num}$. For a predicate
$C$ the provers wish to prove to a verifier that $C(w_1,\cdots,w_{\Num}) = 1$.  
A natural solution for distributed
proof generation is to start with the prover algorithm with a single prover
protocol and run this algorithm between multiple provers using multi-party
computation (MPC). This generic construction was discussed by Pedersen in
~\cite{Ped92}. However, the generic construction is likely to be concretely
inefficient, as implementing high level abstractions such as fields, groups and
generic algorithms like $\fft$ etc to compute the next prover message as an
arithmetic circuit is challenging, and would lead to large circuit
representations. Running multiparty computation over such circuits with several
parties would incur more overheads.
%\nnote{Any numbers to support the above?}
%Each round of proof generation is implemented by an MPC among the provers to
%generate the message to be sent to the verifier.
%The generic construction is optimal in proof size and verifier complexity in that it retains these complexities from the single-prover version irrespective of the number of provers. But, the complexity of proof generation suffers when the single prover protocol is not constructed with distributed proof generation in mind. Even an optimal $\round$-round proof generation algorithm with $O(N)$ multiplicative complexity of the prover's computation might result in a distributed proof generation algorithm with $\Omega(R \cdot N)$ communication among the provers.
To get around the inefficiency of a generic construction, some prior works have
proposed efficient distributed proof generation in restricted settings. These
include simple predicates involved in threshold signatures ~\cite{DDS}, some
sigma protocols ~\cite{EfficientTZ}, combined range proofs ~\cite{bulletproofs},
or under trusted setup with a weaker adversarial model of majority of parties
being honest ~\cite{trinocchio}. The goal of this paper is to address the
aforementioned shortcomings.

We design zero knowledge protocols which enable efficient distributed proof generation, informally an ``MPC-friendly'' proof generation, while supporting \textit{arbitrary} predicates. %The proof generation algorithm is usually measured for efficiency in terms of number of group operations and number of rounds of interaction with the verifier.
Our work first identifies and motivates relevant efficiency parameters that a
zero knowledge protocol should meet to admit efficient distributed proof generation. 
We then construct a zero knowledge 
protocol which is the state-of-art in these parameters. The discussions will
focus on {\em public-coin honest-verifier} protocols with a transparent setup,
which is essentially the setting for real-world applications we envisage: 1) protocols with
such verifiers can be converted to succinct non-interactive  arguments
(zk-SNARGs)  via the Fiat-Shamir and like transforms \cite{FS86, BCS16}, and  2)
generating the parameters of the protocol should ideally {\em not} involve a
trusted third party. The next few subsections elaborate on the new efficiency
parameters, formal definition and our new construction for DPZK that leverages 
a new zero-knowledge argument constructed in this paper, which may be of
independent interest. 

\subsection{Efficiency parameters for $\DPZK$}\label{sec:efficiencyparams}
In the single-prover setting, the efficiency of a zero-knowledge protocol is usually measured in terms of: 
\begin{itemize}
\item {\em prover complexity}, denoted by $t_\prover$, which represents the time
complexity of the prover algorithm,
\item {\em proof/argument size}, denoted by $\zkcomm$ that refers to the amount
of communication from the prover to the verifier,
\item {\em verifier complexity}, denoted by $t_\verifier$, which represents the
time complexity of the verifier algorithm, and
\item {\em round complexity}, denoted as $\zkrounds$, which represents rounds of interaction between the prover and the verifier. %especially when a non-interactive prover is obtained from its interactive version in a provably secure manner \cite{BCS16}.
\end{itemize} 
But, these parameters do not capture the core bottleneck in the setting of multiple provers.  
%For instance, Spartan \cite{spartan} has an $O(N \log N)$ \commentA{unclear; you mean no. of multiplication or overall arithmetic operations? } proof generation algorithm, but due to the high multiplicative complexity of proof generation its straightforward distributed version requires $O(N^2)$ MPC multiplications where $N$ is the number of gates in the circuit representation of the predicate being proved.  \commentA{intuitively explain why the jump from $NlogN$ to $N^2$ happens}%Similar arguments will be made in a future section for the other state-of-art protocols like Aurora \cite{aurora}, Bulletproofs \cite{bulletproofs}. \dnote{mention the asymptotics in the above claims}
As a first step in our work, we identify additional parameters with significant impact in distributed proof generation. A lower value of each parameter enhances the practicality of the
distributed protocol.

\paragraph{Proof-generation communication ($\prcomm$)}
%The first parameter of interest is \textit{proof generation communication} $(\prcomm)$. 
This parameter quantifies the amount of communication between the provers during the
distributed proof generation. This is meant to capture additional MPC
communication that provers would incur while computing the messages to the
verifier. Using secret-sharing based MPC protocols ~\cite{GMW87, BGW88, SPDZ},
this depends on the number of multiplications between inputs from different
parties ({\em cross-multiplications}), that need to be performed to compute the
messages to the verifier. 
%\nnote{Don't we need to motivate why this parameter is important ?}
%In general, this grows linearly with the circuit complexity of the proof generation algorithm for the practical MPC protocols. 
%\nnote{Why are we discussing circuit complexity of proof generation algorithm?}
%\dnote{I am saying "practical" because there are RAM based protocols which do better than circuit complexity of the algorithm.}
%But, there also exist MPC protocols, the secret-sharing based MPC protocols \cite{GMW87, BGW88, SPDZ}, where the communication is only dependent on the number of cross-multiplications i.e., the multiplications between the witness bits from different parties. %This parameter \textit{circuit share complexity}, which we will explain later, will be relevant in many real-world applications. 

%\commentA{section 1.2 should be here, circuit share complexity is related to cross multiplications which is what you talk above. in its current location, it is not clear if it is another parameter of DPZK. If it is, it should be part of this section. To me, it looks like a parameter that impacts both proof generation and proof generation rounds. So after explaining both this parameters, say that we identify a common parameter called 'circuit share complexity' that impacts both in bla bla way. But the above four parameters will be the ones we use for stating the complexity of our protocols and for the purpose of comparison  }
%, since an affine function over the witnesses and a multiplication between witness bits from the same prover can be computed without any interaction in a secret-sharing based MPC.

\paragraph{Proof generation rounds ($\prrounds$)}
%The next parameter of interest is the number of \textit{proof generation rounds ($\prrounds$)} which 
This indicates the number of rounds of communication between the provers during
the distributed proof generation. Informally, it denotes the number of rounds the provers need to run MPC protocols. %separate MPCs that the provers have to run throughout the proof generation process, times the number of interactions needed inside each 
 This is orthogonal  to $\zkrounds$ and may not have any correlation with it. % Note that this could be lower than the round complexity of the zero knowledge protocol. 
%\nnote{Do we really need the discussion below? What is the conclusion?}
%{\color{blue} In a typical MPC, this parameter would be a constant number for
%the garbled-circuit based protocols and be the cross-multiplicative depth of the
%circuit for the secret-sharing based protocols. But in our setting of
%distributed proof generation, the provers have to compute their message for that
%round, in clear, to be sent to the verifier. Thus, even a garbled-circuit based
%approach here might result in $\prrounds$ be linear in the number of
%$\zkrounds$, and hence not a constant with respect to the size of the instance
%unless $\zkrounds$ is also a constant.} 
%\commentA{it's hard to digest the above; what's the point you are trying to make; some of the zkRounds do not need MPC and hence we can get read of the linear independence of prRounds from zkRounds?  }
%\dnote{The above point makes sense only for the interactive version. Should we also argue for non-interactive proof generation?-that it requires us to do hash inside MPC if MPC is not done for each step.} 
%\commentA{I didn't understand your comment. other can help?}
The parameter $\prrounds$ is also of cryptographic interest. If there is more than one round of prover message generation which requires MPC, care has to be taken to ensure a secure composition of the individual MPCs to prove the complete protocol is secure.

\paragraph{Shared circuit complexity}
We will now elaborate a bit more on the number of cross-multiplications in the circuit that needs to be evaluated distributedly for proof generation since
that is of practical relevance and influences prover communication ($\prcomm$)
and proof generation rounds ($\prrounds$). In applications where the initial
witness is canonically \textit{partitioned} among the provers, the term
\textit{shared circuit} denotes sub-circuit consisting of wires, whose 
values are functions of inputs from more than one prover. 
Consider the earlier example of a trade-logistics business network, now on top of 
a blockchain where the hashes (or any other commitment) of large number of data points
from different participants are stored. 
When parties come together to prove a statistic on their combined data, they
need to establish that each data point used to compute the statistic corresponds to a 
hash entry in the blockchain, and the correctness of the result of the statistic
computation on these data points. But here, the values of the circuit wires
connecting each data point to its respective hash depends only on witness bits from a 
single party which owns the data point. Only the part of the circuit computing the 
statistic takes witness bits from multiple parties, and thus only this part
needs to be considered for MPC while computing shares of extended witness. It
would be desirable, though not evident, that the complexity of the MPC for {\em proof
generation} also depends favorably on the size of the shared circuit. 
With the standard SHA hash function having around 30,000 gates, the practicality of 
distributed proof generation will be
greatly improved if its parameters (like $\prcomm$ and $\prrounds$) are 
linear in the size of the shared circuit $N_s$ and not the total circuit size $N$.
%Looking ahead, the complexity of the interaction between the provers in our DPZK protocol will be linear only in the circuit share complexity of the circuit predicate to be proven, and not in the total size of the circuit. 

In summary, the efficiency of a DPZK in the public-verifiable and
non-interactive setting (which is our concern) will be measured via $\prcomm$,
$\prrounds$, in addition to the parameters for the single prover protocol.

\subsection{On the formal Definition of $\DPZK$}
%\commentA{changed the title of this subsection and the text below sightly} 
%The primary departures that the security definition of $\DPZK$ witness compared to the  traditional single-prover ZK are concerning the zero-knowledge property.     
%Before we delve into our DPZK construction, we would also provide a couple of subtle notes regarding the zero-knowledge property of DPZK protocols. This would shed some light on the rationale for some of the artefacts of DPZK protocols. 
%In an $\DPZK$ protocol, the verifier is allowed to collude with a subset of provers to learn the witnesses of the other provers. A strong definition of zero-knowledge should ensure that this collusion does not learn any additional information than what they know before the protocol. %Here, one should also consider the number of other provers involved in the proof generation as an additional information. In our protocols, we will allow all the provers to know the total number of provers involved. This will lead to a relaxed definition where a verifier colluding with a prover will additionally learn the total number of provers\pnote{usage of broadcast reveals the number of provers even without collusion}. This still does not let a standalone verifier learn the total number of provers during its interaction with the provers.

%\commentA{I am not finding the following paragraph pressing. Should we remove? }\dnote{This is to emphasize the need for public key ops or communication in oracle generation/answering too. I cut it short though.}
%This subtle note also impacts the size of the oracles for the protocols in the IOP framework \cite{aurora, ligero}. The oracle and the answers to the oracle queries should be independent of the total number of provers. Hence, for the IOP-based protocols, the efficiency parameters discussed above should be optimized not only for the prover message generation but also for the oracle generation and the query answering.\footnote{In principle, generating the oracle or answering a query would form a part of the prover message generation when IOP is viewed in the lens of an arbitrary interactive protocol.}
%The IOP-based protocols in the literature \cite{aurora, ligero} market their non-use of public-key cryptography and thus a potential post-quantum security feature. To achieve zero-knowledge in the distributed prover setting while retaining these features, at a high level, they have to incur the additional overhead in $\prcomm$ due to using information-theoretic MPC to also construct the oracle and answer oracle queries. 

%Another subtle point here is that a single-prover ZK protocol provides the zero-knowledge property only for honest provers. The witness is not guaranteed to be hidden from the verifier if a prover deviates from the protocol. Hence, in a distributed prover setting it is non-trivial to prove or even define the zero-knowledge property if some of the provers deviate from the protocol or if they do not have the valid witness. 

Just like the efficiency considerations, the security definition for a DPZK
protocol needs to account for additional interaction. In particular, the
security definition needs to capture the fact that interaction among the provers
to generate the proof does not leak knowledge about their respective witnesses
to other provers. 
We come up with an MPC-style definition based on real-world ideal world paradigm \cite{Canetti00,Goldreich2001,Lindell17,CohenL14}  that takes the above issues into account. In the ideal-world, the provers deliver their respective part of the witnesses and the functionality (that is parametrised with a language) combines them and check the assertion of a statement. In the real protocol,  the provers participate in  instances of MPC for `proof-generating functions' to generate messages for the verifier. To  keep the proof-size  independent of the number of provers, one of the provers enacts in a special role called aggregator   that prepares the message for the verifier taking into account communication from all its fellow provers and communicates the same to the verifier on behalf of all the provers. We say our protocol is secure if whatever an adversary (corrupting various subset of provers and verifier) can do in real execution can be done in the ideal execution. Lastly, keeping in mind the final goal of non-interactive and publicly-verifiable proofs/arguments, we explicitly mention the exact corruption scenario that we handle for our constructions.  For example, it is enough to tackle a semi-honestly corrupt verifier (since a non-interactive proof does not give any additional scope of misbehaviour to a maliciously corrupt verifier  over a semi-honestly corrupt one).  We refer to Section~\ref{sec:security model} for complete details. Next, we move on to discuss the single-prover construction on which we build our DPZK. 
To preserve the privacy, we assume that provers are not going to deviate from the protocol, since that may lead to rejection of the proof, though our protocol can withstand the scenario if all the provers are maliciously corrupt together due to the soundness property of the underlying ZK protocol.% Also, we will discuss how can we achieve security against maliciously corrupt provers (assuming the aggregator \commentA{we have not introduced aggregator} to be semi-honest). hide the number of provers from a corrupt verifier and to

\subsection{\name{}: an MPC-friendly zero-knowledge protocol}
We present an MPC-friendly single-prover protocol \name{} with a transparent setup which
allows an efficient  DPZK.
%This linear $\prComm$ is due to linear number of cross-multiplications which can be done concurrently, and hence the MPC is only performed on an $N$ mult-gates circuit of depth 1. 
\name{} achieves proof size and verification complexity competitive with the
state-of-art zero knowledge protocols, while achieving efficient distributed
proof generation. In particular, for a statement represented as a circuit with $N$ multiplication gates,
\name{} admits a proof size of $O(N^{1/c})$ for
arbitrary $c\geq 2$, with a verification complexity of $O(N^{1-2/c})$ public key
operations and $O(N)$ field operations. \name{} is a public-coin, honest verifier
zero-knowledge protocol in the Interactive PCP (IPCP) \cite{KR08, KR09, GIMS10,ligero}
paradigm. In IPCP paradigm, the verifier reads a small number of bits from PCP created by the prover and exchanges a small number of bits with the prover.
There is known transformation that converts ZK designed with IPCP to an interactive ZK via collision-resistant hash functions \cite{IshaiMS12, IshaiW14} which in turn can be made non-interactive  \cite{FS86, BCS16}. 

% that achieves the property of zero-knowledge-with-collusion i.e.,
%the witnesses from a set of provers are not revealed to a verifier even when it
%colludes with the complimentary set of provers who are honest-but-curious.

%Efficiency Desiderata:  
%- Transparent setup 
%- Minimum interaction between the provers (\# of rounds of MPC) 
%- Total communication complexity of the msgs exchanged
%- verifiers view is indistinguishable from a single prover setting
%- How efficient is underlying zkp protocol (public key operations, size of proof, prover/ verification time)
%- Applicability to a general class of computation

%\paragraph{Technical overview}
%Our goal is construct a zero-knowledge protocol which optimizes all the efficiency parameters: $\zkcomm$ a.k.a., the proof size, $\zkrounds$, provers' complexity (represented by $\prcomm$ and $\prrounds$) and the verifier's complexity. We will now brief the MPC (non-)friendliness of the state-of-art protocols in the setting before we brief \name{}.
%
%Also, its verifier requires $O(N)$ public key operations to verify a proof. 
%Spartan \cite{spartan} admits sublinear verifier complexity in an amortized sense, but its prover again incurs $O(N^2)$ multiplications.

\name{} follows the broad outline of Ligero~\cite{ligero}: 
(i) encoding the `extended' witness via a suitable error-correcting code, where the extended witness is the concatenation of the wire values of the circuit (for the statement) in a topological order evaluated on the witness, (ii) using the
encoding to check linear and quadratic relations on the extended
witness, and (iii) a check to ensure that the extended witness is correctly
encoded. The extended witness (henceforth witness) encoding is committed as an ``oracle'' and is queried
during the linear and quadratic checks.  Our key innovations are
listed below. 

\paragraph{New encoding and oracle} A core technical contribution of our
work is a novel way to encode the witness and design the three checks in
the zero-knowledge protocol around the new encoding. The \textit{witness} is
represented as a \textit{3D matrix} of dimensions $p \times m \times s$ whose
product is $O(N)$. The \textit{witness encoding} is obtained by encoding every
$m \times s$ `slice' of the 3D matrix using a carefully selected product of
Reed-Solomon codes.  The \textit{oracle} is now obtained by committing each $O(m)$-sized `column' in 
the encoded witness using homomorphic vector commitments \cite{Ped92}. 
This results in an oracle that is a $O(p \cdot s)$-sized matrix of commitments.
The use of homomorphic vector commitments helps in two aspects: (i) enabling
distributed proof generation and (ii) achieving proof sizes independent of the
largest dimension of the matrix. The latter is crucially dependent on the use
of product codes to achieve soundness with very small {\em query complexity} (the size of the
oracle revealed to the verifier).
As we will see later, we will be able to regulate the three dimensions such that
both the communication between the provers and the
aggregator and that between aggregator and the verifier (argument size) are 
{\em sub-linear} in circuit-size $N$.  \commentA{can you point out the coding theory result below. it was in the earlier version. seems to get washed out. made a blunt attempt below. refine} Lastly, the fact that a malicious prover is forced to make an oracle that corresponds to
a well-formed witness encoding leverages a new result in coding theory, which appear in Section~\ref{new_result_coding_theory} and proof is given in Appendix ~\ref{app:ProofofLem3dcompression}. 

\paragraph{Checking Linear and Quadratic Relations} As in other oracle-based protocols~\cite{ligero,aurora}, checking the linear and quadratic relations on the witness reduces to 
 checking identities on the polynomials derived from polynomials encoding the witness. 
To ensure that the size of the final polynomial, which can be shared with the verifier is
proportional to the smallest dimension of the three dimensional witness matrix,
we need to achieve two stages of ``compression''. To ensure soundness for both
stages of compression, we introduce an intermediate structure (a two dimensional
matrix) to which the prover commits. This intermediate matrix enforces
consistency between the three dimensional encoding, and one dimensional
polynomial message to the verifier as it can be checked to be consistent with
both. Having an extra dimension (over Ligero) also allows us to shave off the size of the
largest dimension over which we run (expensive) inner-product arguments. This
allows us to achieve inner-products over vectors of size $N^{1-2/c}$, which
makes our verifier quite efficient despite using public key operations. These
protocols appear in Section~\ref{sec:graphene}.


\subsection{\dpname: A new $\DPZK$ protocol}
%\commentA{The structure of this section should be as follows:  (a) state what the extract result for $\DPZK$, mentioning the achieved complexities (can plug in the best-known MPC)  (b) tell the high level idea for the approach taken. be concise (c) tell about the difficulties in turning existing spzks to DPZK (d) compare and put the table with asymptotic complexity; (e) report some  of the numbers that we obtain from benchmarking.  }
Building on \name{}, we design our DPZK protocol \dpname{} with  $\prcomm$ linear in size of the $\npol$ verification circuit for the language and with a constant $\prrounds$. To be more precise, the communication for a
$\Num$-prover proof generation for an $N$-multiplication gate circuit 
would be $O(\Num^2\cdot N_s + \Num \cdot N^{1-2/c})$, where
$N_s$ is the shared circuit size as introduced in Section
~\ref{sec:efficiencyparams}. Moreover, although $\zkrounds$ is $O(\log{N})$, $\prrounds$ is constant, limited to a single instance of secret-sharing based MPC on a circuit
of size $\max(N_s,N^{1-1/c})$ and multiplicative depth as $1$. To emphasize the non-trivial properties attained
by our protocol, we discuss the roadblocks in naively adapting existing
state-of-art zero-knowledge protocols to the distributed prover
setting.\smallskip

\noindent{\em Roadblocks in achieving DPZK}: Intuitively, to satisfy the desiderata
of distributed proof generation with minimal prover communication, large parts
of the messages to the verifier must be computable {\em locally} by the provers
using their respective shares of the witness, which then must be efficiently 
aggregatable later to obtain the final message. Thus, the prover messages must have some
``homomorphic'' properties with respect to the witness. This requirement
precludes naively extending recent efficient zero-knowledge protocols based on
interactive oracles like \cite{ligero,aurora}. Realizing the oracle while constructing a non-interactive
argument in the Random Oracle Model (ROM) uses hash functions, which exhibit no such
homomorphic properties. We address this roadblock in our construction by making
the oracle homomorphic. However, constructing such an oracle incurs expensive
public key operations for the prover. For the restricted case of IPCP, where
only the initial message is an oracle, the additional overhead though
substantial is tolerable. For more general interactive oracle protocols, such as
Aurora ~\cite{aurora}, our methods may not be the most efficient. Nevertheless,
we pose efficient DPZK construction from general interactive oracle protocols as an
interesting open question. Even if the messages in the protocol are largely
homomorphic, small amount of non-homomorphic computation in several rounds 
would require repeated interaction among the provers. Intuitively, one way to
avoid repeated prover interaction is to reduce the initial statement, to a
statement involving ``random witnesses'', which can then be ``handed off'' to the
aggregator to complete the remaining rounds of interaction with the verifier. It is essential that
the witnesses in the reduced statement are ``random'' or ``simulatable'' to
ensure that the aggregator gains no knowledge of provers' witnesses from them.
In general, in such constructions one must ensure that in addition to verifier's
view, the aggregator's view also leaks no knowledge. We did not see an obvious
way to overcome this roadblock for Spartan ~\cite{spartan}, without resorting to
expensive MPC among the provers. Among the existing zero-knowledge protocols, we
were only able to obtain an efficient DPZK from Bulletproofs
~\cite{bulletproofs} with moderate effort. This construction appears in Appendix ~\ref{app:BulletproofsDPZK}
%{\color{blue} (Put appropriate section)}, 
and serves as a baseline for
comparison with $\dpname$. Even for the Bulletproofs based construction, we are
unable to achieve sub-linear prover communication for a sub-linear shared circuit
size $N_s$. We extensively compare the two constructions across both the DPZK
parameters, and the single prover parameters in Section
~\ref{sec:performancecompare}.
  
Finally, we mention that the provers in \dpname{} are semi-honest in trying to learn 
each other's witnesses while constructing messages for the verifier. This view
fits well with the kind of applications we forsee, where incentive to make a
joint claim is greater than that to deviate from the protocol.
Even for this weaker adversarial model, proving the security of this
construction is interesting because of a couple of reasons. The witness shares
that the provers start with are additive, but they need not be from a secret
sharing of a ``global'' witness. And, even if the provers' shares are secret
shares of a global witness with a threshold of $\Num-1$, the aggregator in our
construction sees messages from \textit{all} the $\Num$ provers. We prove the
security of \dpname{} taking care of these aspects when the provers and the
aggregator are semi-honest.
\dnote{insert benchmarking numbers for \dpname{}
here}

%\footnote{Our DPZK-Bulletproofs construction supporting
%arbitrary predicates readily follows from their single-prover construction, even
%though they mention it as an open problem to support arbitrary predicates after
%they build a distributed proof generation algorithm for range proofs. Our
%efforts simply distil the multiplicative parts of their inner-product protocol.
%\pnote{Bulletproofs proof aggregation is not same as distributed proof
%generation.}} \dnote{is the phrasing in the footnote fine?}

%Each prover in \dpname{} starts with an additive share of the witness. Each prover generates an encoding of its witness using the same procedure as in \name{} due to the additive homomorphism in Reed-Solomon encoding and in oracle generation. \dnote{seems like we have to add slightly more details in the description of \name{} so that we can refer to it here to explain the dpzk construction. @Nitin can you take a shot at this paragraph after you augment the technical overview?}


%\subsection*{Distributed proof generation}
%--- Informal notion of Distributed Provers Zero Knowledge Protocol $\innp{\Pi}{\verifier}$--- 
%
%A na\"ive approach to build a $\DPZK$ protocol is to take a single-prover ZK protocol and execute a multi-party computation among the provers of each message to be generated by the prover in the single-prover protocol. This satisfies the required security properties, but suffers in concrete efficiency when MPC is used over the proof generation as a black box. 
%
%\subsubsection*{Need for homomorphic commitments} 
%(Oracle access for IOP).
%The (non-interactive) zero-knowledge proof generation protocols based on the Interactive oracle proofs (IOP) or the Interactive PCP (IPCP) paradigms make use of \textit{oracles}. The prover establishes an oracle based on her witness. Once established, the IOP/IPCP protocols ensure that a prover will not modify the oracle further in the protocol. The verifier queries the oracle later in the protocol to verify some the claims made by the prover. When IOP/IPCP based proof systems are converted into the non-interactive setting, the establishment of the oracle is done by producing a commitment to the oracle entries.
%
%We will now run through a mental experiment on achieving distributed proof generation following the blueprint of the single-prover proof generation algorithm. We desire to not have the proof length depend on the number of parties. As we would discuss in depth later, we would also avoid running an MPC protocol on the proof generation circuit(s) of some zero-knowledge protocol. This would trivially, in theory, satisfy our goals, but it would be very inefficient in practice. The way we satisfy these goals for the establishment of the oracle is by requiring the oracle entries and their commitments satisfy homomorphic properties.
%\dnote{self: Sounds somewhat weak. Make it more compelling.}
%
%\subsection*{Technical summary}
%We will now provide a high-level summary of our work and along the way mention our core ideas.
%
%%Our contributions are two-fold: first in defining and constructing a zero-knowledge protocol with distributed proof generation and the second in proposing the first protocol with (expected) sub-linear verifier complexity.
%
%Our main contribution is defining and constructinf a zero-knowledge protocol with distributed proof generation.
%
%\paragraph{DPZK}
%We design a framework for constructing DPZK protocols starting from a single-prover ZK protocol.
%%To construct our DPZK protocol \name{} we follow the strategy of designing a (public coin honest verifier) single-prover ZK protocol whose proofs are ``aggregatable'' at minimal cost. 
%Let the parties $\prover_1, \ldots, \prover_{\Num}$ hold their respective witnesses $\wit_1, \ldots, \wit_{\Num}$ to the relation $R(\stmt, (\wit_1, \ldots,\wit_{\Num}))$. 
%Starting with a (public coin honest verifier) single-prover ZK protocol, there are two steps involved in our proof generation.
%\begin{itemize}
%\item The first step involves performing a secret sharing based MPC protocol on $R$ between the provers. As a result, each prover obtains her share of the extended witness, which includes all the wires (correspondingly variables) of a circuit (correspondingly R1CS) representation of R. 
%\item Next, for each message from the prover to the verifier, the parties perform the following two steps:
%\begin{itemize}
%\item The parties run an MPC protocol to obtain their share of the message. This step has a major implication on the efficiency of distributed proof generation. Depending on the single-prover protocol, some messages already posses homomorphism properties. Hence, the output of a local run of the single-prover algorithm for this round on a prover's shares of extended witness is already her share of the message in the distributed proof generation. When the message is not homomorphic, we design custom efficient protocols to obtain the shares of the message.
%\item One of the prover parties or an external entity trusted with the correctness of execution is chosen as an ``aggregator''. Aggregator is not trusted with the privacy of the inputs. The aggregator receives the shares of the messages from all the parties and performs the steps of the single-prover protocol to be performed with the aggregated message. Also, a prover acting as an aggregator does not have an incentive to deviate from executing the correct protocol during this step. This is because she could have caused the protocol to abort in any of the previous steps, and there is no additional information that she gains in the intermediate steps that aids her deviation in the aggregation step.
%\end{itemize}
%\end{itemize}
%
%Starting with the single-prover protocol of \cite{ours}, we design custom protocols so that the only additional interaction between the parties during the second step involves MPC for $\intpartofC$ concurrent multiplications, where $\intpartofC$ is the number of wires in the \textit{interactive} part of the circuit. Consider the check $x+y \stackrel{?}{=} z$ when given their respective hashes. If the inputs are present with three different parties, the corresponding circuit for the hash check followed by the addition and equality check involves extensive local computations for the hash before the interaction happens. \dnote{self: Provide a compelling real world use-case here} The additional communication complexity of our $\DPZK$ protocol grows only with the size of the interactive part. To enable this, we do.... start with \cite{ours} --- arrange the rows accordingly in the witness matrix --- 
%
%proof size independent of number of parties --- Oracle queries outputs should be independent of the number of parties --- we do it having parties generate a homomorphic oracle starting with their shares on the extended witness --- we would achieve indistinguishability between proof generated in a distributed manner and the proof generated by a single party ---
%In this, we use homomorphic commitments --- we follow from \cite{ours} --- 


\input{Related_work.tex}
%Let $P$ be the predicate that is being proved. An aggregation of multiple proofs on the same $P$ produces a proof.  Let us consider the interactive version of the protocol. A proof consists of the messages sent by the prover to the verifier and, additionally in IOPs, the replies to the oracle queries of the verifier.
%where each message from the prover is first identified whether it is homomorphic or not. If 
%each prover can produce an additive share of the proof.  find a way to \textit{aggregate} the proof parts from each prover. identify the prover messages which are homomorphic.
%
%the goals that we set for our construction
%
%the theme that we will have - require every message from prover to verifier be homomorphic.
%
%concrete starting point - ligero --- 
